### 2010-11-08 docs/tex/mimicry.tex
Mimicry chapter mostly complete

\section{Evolutionary Dynamics of Mimicry}
There has been many explanations on the dynamics of mimicry.

The dynamics of mimicry has been explained in detail by Turner, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism. As Turner states,

@@

\subsection{Mimicry Ring}

\subsection{Formation of Mimicry Rings}

\section{Other form of mimicry}

\section{Conclusion}

>>>>

\section{Evolutionary Dynamics of Mimicry}
The dynamics of mimicry has been investigated by Turner \cite{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.

\paragraph{Punctuated Equilibrium}
Punctuated equilibrium is a theory in evolutionary biology which proposes that most sexually reproducing species will experience little evolutionary change for most of their geological history, remaining in an extended state called \textit{stasis}. When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis. Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another. Thus, ``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}.

\paragraph{Phyletic Gradualism}
In contrast to punctuated equilibrium, phyletic gradualism states that species continue to adapt to new environmental and biological selection pressures over the course of their history, gradually becoming new species. Phyletic gradualism holds that a species population changes gradually; that is there is no clear line of demarcation between an ancestral species and a descendant species unless a splitting (cladogenetic) event occurs or the gradually-changing lineage is divided arbitrarily. During this process, evolution occurs at a smooth, steady and incremental (but not necessarily constant and slow) rate on a geological time scale.

On this issue Turner states,

@@

To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \cite{turner1988}, which was originated by Poulton \cite{poulton1912} and Nicholson \cite{nicholson1927}, termed as the \textbf{two stage model}. This theory states that mimicry normally arises in two steps. A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \cite{sheppard1972} \cite{ford1964}. This two-stage theory has been for the explanation of Mullerian mimicry as well.

\subsection{Mimicry Ring}
Any theory of Mullerian mimicry has to take into account the phenomenon of the coexistence of multiple mimicry rings. If we examine the local butterfly fauna in any area of the world, we will find that between all the aposomatic (warningly colored and defended) species present there are normally only a limited number of different patterns, normally far smaller than the number of species. Each cluster of species, all sharing a common pattern, is termed as Mullerian mimicry ring. Thus, in the rain forest of South and Central America, most of the long-winged butterflies (ithomiids, danaids, and heliconids) belong to one of only five different rings.

\subsubsection{Formation of Mimicry Rings}
In regards to the formation of mimicry ring Turner \cite{turner1988} has given a theory which takes into account the level of protection of different rings of butterfly species and their difference in phenotypic warning patterns. Different level of variation of these two parameter can give us very different formation of mimicry ring evolution. The cases are considered below.

\begin{itemize}
	\item If we imagine two different rings of similar warning patterns in one single habitat, similar enough that the envelop of protection afforded to one gives some protection to the more extreme variant of the other (in a simplified language, suppose that predators that have sampled species A sometimes avoid the more extreme members of species B because they mistake them as A), then these two species are subject to natural protection for mutual convergence of their patterns. Eventually they will form a rather accurate Mullerian mimicry ring.
	\item By contrast, if the two species have patterns so dissimilar that predators encountering one never imagine that it might be the other (the envelop of protection do not overlap the other species' phenotype distribution), then there is no selection whatever for convergence, and the two patterns will remain distinct indefinitely.
 \item But mutations of color patterns are occurring all the time. Suppose that species B happens to produce a mutation whole pattern falls within the envelop of protection afforded to species A. The mimicry need not be perfect, but if it is good enough, the mutation will have an advantage and will spread. In this way species B may, by a single mutation, become a Mullerian mimic of species A; in other word species B may switch from one Mullerian mimicry ring to another. Clearly, if the mimicry is not perfect, the two patterns will then gradually converge, making the resemblance ever closer. 
\end{itemize}

Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage. It is worth mentioning that in the first stage only the less protected species can adopt the pattern of the better protected species; mutations in the other direction is not favored.

\section{Conclusion}
Mimicry is one of the most fascinating cases of evolutionary biology. This phenomenon has been studied extensively as infinite number of evidence exists in nature. One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it. And this figure has been taken from Wilcker \cite{wickler1986} which has been published in 1986. It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless. Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \cite{cott1957}.
